`````{r}
rm(list=ls())
library(tidyr)
library(dplyr)
library(ggplot2)
library(langcog) 
library(rjson)
``````

````{r}
path <- "~/Box Sync/mturk/"
files <- dir(paste0(path,"sandbox-results/"), 
             pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste0(path, "sandbox-results/",f)
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId,
                   cond = jd$answer$data$cond,
                   first_offer = jd$answer$data$first_offer,
                   power=jd$answer$data$power,
                   control =jd$answer$data$control,
                   strong = jd$answer$data$strong,
                   confident =jd$answer$data$confident,
                   sex =jd$answer$data$sex,
                   age = jd$answer$data$age,
                   nat = jd$answer$data$nat,
                   lang = jd$answer$data$langu,
                   eth = jd$answer$data$eth,
                   AC= jd$answer$data$AC)
                   
  
     d.raw <- bind_rows(d.raw, id)
}
          
               